### 2022-03-22 README.Rmd
README now presents the outputs. EL2 class uses gradient for convergence check. This is experimental. Now, the version is 1.2.0.9000
gbd related functions kind of sandboxed
EL class redesigned. convergence criterion updated. threshold is available.
abstol replaced by tol

## Installation
You can install the latest stable release from [CRAN](https://cran.r-project.org/package=melt).
```{r eval = FALSE}
install.packages("melt", dependencies = TRUE)
```
You can install the latest development version from
[Github](https://github.com/markean/melt).
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("markean/melt")
```

## Usage
```{r eval = FALSE}
library(melt)
# one sample test (mean)
el_mean(par = 0, x = rnorm(n = 100))

>>>>

## Installation
You can install the latest stable release from [CRAN](https://cran.r-project.org/package=melt).
```{r eval = FALSE}
install.packages("melt")
```
You can install the latest development version from
[Github](https://github.com/markean/melt).
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("markean/melt")
```

## Usage
```{r eval = TRUE}
library(melt)
# one sample test (mean) 
el_mean(par = 0, x = rnorm(n = 100))
